Adversarial Training against Systematic Uncertainty

### 2016-09-06 tex/paper.tex
typo

\begin{proof}
The optimal parameters $\smash{\hat\theta}_r =
\arg \max_{\theta_r} E(\theta_f, \theta_r) = \arg \min_{\theta_r} L_r(\theta_f,
\theta_r)$ are such that $p_{\theta_r}(z|f(X;\theta_f)) = p(z|f(X;\theta_f))$.
By assumption, $p_{\theta_r}(z|f(X;\theta_f)) = p(z)$,
and therefore $p(z|f(X;\theta_f)) = p(z)$.
Using the Bayes' rule, we write
\begin{align*}
    p(f(X;\theta_f)|z) &= \frac{ p(z|f(X;\theta_f)) p(f(X;\theta_f)) } { p(z)} = p(f(X;\theta_f)),
\end{align*}
which holds for all $z \in {\cal Z}$ and implies that $f$ is a pivotal quantity.
\end{proof}

@@

\begin{proof}
For fixed $\theta_f$, the adversary $r$ is optimal at $\hat\theta_r = \arg
\max_{\theta_r} E(\theta_f, \theta_r)  = \arg \min_{\theta_r} L_r(\theta_f,
\theta_r)$, in which case $p_{\theta_r}(z|f(X;\theta_f)) = p(z|f(X;\theta_f))$ and $L_r$ reduces to the entropy
$H(p_{Z|f(X;\theta_f)})$ of the conditional distribution of the nuisance. The
value function $E$ can therefore be rewritten as $$E'(\theta_f) = L_f(\theta_f) -
H(p_{Z|f(X;\theta_f)}).$$  In particular, we have the lower bound $H(p_{Y|X}) -
H(p_Z) \leq L_f(\theta_f) - H(p_{Z|f(X;\theta_f)})$ where the equality
holds at $\smash{\hat\theta}_f = \arg \min_{\theta_f} E'(\theta_f)$ only when
\begin{itemize}
    \item $\smash{\hat\theta}_f$ corresponds to
    the parameters of an optimal classifier, in which case the expected negative log-likelihood $L_f$ of $Y|X$
    reduces to its minimum value $H(p_{Y|X})$,
    \item all
   outcomes of $Z|f(X;\smash{\hat\theta}_f)$ are equally likely, in which case
   $p(z|f(X;\smash{\hat\theta}_f)) = p(z)$ for all $z \in {\cal
   Z}$ since we require a uniform prior by construction. Note that in the continuous case, the supremum of the differential entropy
   over continuous distributions on the same bounded support is also realized by the uniform distribution over that support.
\end{itemize}
Accordingly, the second condition implies that $p_{\theta_r}(z|f(X;\theta_f)) = p(z)$ and therefore that at this
point, because of Proposition~\ref{prop:1}, the optimal classifier $f(\cdot;\smash{\hat\theta}_f)$ is also a pivotal quantity.
\end{proof}

@@

\glnote{We should further discuss that in practice, the equality in Prop 2 may never hold.
We should discuss in which circumstances. In such case, the pivotal quantity
constraint can however be enforced by outweighting the $L_r$ term, resulting in a
trade-off between classifier optimality and pivotality.}

>>>>

\begin{proof}
The optimal parameters $\smash{\hat\theta}_r =
\arg \max_{\theta_r} E(\theta_f, \theta_r) = \arg \min_{\theta_r} {\cal L}_r(\theta_f,
\theta_r)$ are such that $p_{\theta_r}(z|f(X;\theta_f)) = p(z|f(X;\theta_f))$.
By assumption, $p_{\theta_r}(z|f(X;\theta_f)) = p(z)$,
and therefore $p(z|f(X;\theta_f)) = p(z)$.
Using the Bayes' rule, we write
\begin{align*}
    p(f(X;\theta_f)|z) &= \frac{ p(z|f(X;\theta_f)) p(f(X;\theta_f)) } { p(z)} = p(f(X;\theta_f)),
\end{align*}
which holds for all $z \in {\cal Z}$ and implies that $f$ is a pivotal quantity.
\end{proof}

@@

\begin{proof}
For fixed $\theta_f$, the adversary $r$ is optimal at $\hat\theta_r = \arg
\max_{\theta_r} E(\theta_f, \theta_r)  = \arg \min_{\theta_r} {\cal L}_r(\theta_f,
\theta_r)$, in which case $p_{\theta_r}(z|f(X;\theta_f)) = p(z|f(X;\theta_f))$ and ${\cal L}_r$ reduces to the entropy
$H(p_{Z|f(X;\theta_f)})$ of the conditional distribution of the nuisance. The
value function $E$ can therefore be rewritten as $$E'(\theta_f) = {\cal L}_f(\theta_f) -
H(p_{Z|f(X;\theta_f)}).$$  In particular, we have the lower bound $H(p_{Y|X}) -
H(p_Z) \leq {\cal L}_f(\theta_f) - H(p_{Z|f(X;\theta_f)})$ where the equality
holds at $\smash{\hat\theta}_f = \arg \min_{\theta_f} E'(\theta_f)$ only when
\begin{itemize}
    \item $\smash{\hat\theta}_f$ corresponds to
    the parameters of an optimal classifier, in which case the expected negative log-likelihood ${\cal L}_f$ of $Y|X$
    reduces to its minimum value $H(p_{Y|X})$,
    \item all
   outcomes of $Z|f(X;\smash{\hat\theta}_f)$ are equally likely, in which case
   $p(z|f(X;\smash{\hat\theta}_f)) = p(z)$ for all $z \in {\cal
   Z}$ since we require a uniform prior by construction. Note that in the continuous case, the supremum of the differential entropy
   over continuous distributions on the same bounded support is also realized by the uniform distribution over that support.
\end{itemize}
Accordingly, the second condition implies that $p_{\theta_r}(z|f(X;\theta_f)) = p(z)$ and therefore that at this
point, because of Proposition~\ref{prop:1}, the optimal classifier $f(\cdot;\smash{\hat\theta}_f)$ is also a pivotal quantity.
\end{proof}

@@

\glnote{We should further discuss that in practice, the equality in Prop 2 may never hold.
We should discuss in which circumstances. In such case, the pivotal quantity
constraint can however be enforced by outweighting the ${\cal L}_r$ term, resulting in a
trade-off between classifier optimality and pivotality.}
